\Title

### 2021-03-29 latex/paper/main.tex
First rough draft of the experiments section

%/========== Simulation ==========/%
\section{Simulation Results}\label{sec:simulations}
\textbf{Run a sim of a simplfied acrobot model of a human}
%/========== Experiments ==========/%
\section{Experimental Results}\label{sec:experiments}
In this section, we test our VNHC on the physical acrobot built by
Xingbo Wang \cite{xingbo_thesis} (Figure \ref{fig:xingbo-acrobot}).
The torso and leg rods on this robot have unequal mass and differ in length, so
its inertia matrix and potential function are not described correctly by 
~\eqref{eqn:acrobot-inertia}-\eqref{eqn:acrobot-potential}.
These experiments will therefore show that VNHCs are robust to model mismatch.

@@

The leg actuator is a servo motor with a built-in PID controller, so we
can directly assign \(q_a = \arctan\left(I p_u\right)\).
The control parameter \(I\) must be small to satisfy Theorem
\ref{thm:acrobot-energy-stabilization}, but it must also be large enough to
overcome friction in the servo motor.
We experimentally determined that \(I = 10\) is sufficient to
ensure the actuator can fully rotate in its allowable range
\(q_a \in \left[ -\frac{\pi}{2}, \frac{\pi}{2}\right]\).
%/========== Proof ==========/%
\section{Proof of Theorem \ref{thm:acrobot-energy-stabilization}}\label{sec:proof}

%/========== Conclusion ==========/%
\section{Conclusion}\label{sec:conclusion}

>>>>

%/========== Experiments ==========/%
\section{Experimental Results}\label{sec:experiments}
In this section, we test our VNHC on the physical acrobot built by
Xingbo Wang \cite{xingbo_thesis} (Figure \ref{fig:xingbo-acrobot}).
The torso and leg rods on this robot have unequal mass and differ in length, so
its inertia matrix and potential function are not described correctly by 
~\eqref{eqn:acrobot-inertia}-\eqref{eqn:acrobot-potential}.
These experiments will therefore show that VNHCs are robust to model mismatch.

@@

The control parameter \(I\) must be small to satisfy Theorem
\ref{thm:acrobot-energy-stabilization}, but it must also be large enough to
overcome friction in the servo motor.
We experimentally determined that \(I = 10\) is sufficient to
ensure the actuator can fully rotate in its allowable range
\(q_a \in \left[ -\frac{\pi}{2}, \frac{\pi}{2}\right]\).

\subsection{Simulations Results}
Evaluating the true mechanical energy of Wang's acrobot at the VNHC
\(q_a = 0\) yields the energy of the nominal pendulum,
\[
    E(q_u,p_u) \approx 396.5501 p_u^2 + 0.5997(1 - \cos(q_u))
    .
\]
We simulated Wang's acrobot starting at 
\((q_u,p_u) = \left(\frac{\pi}{32},0 \right)\) and plotted the resulting orbit
in Figure \ref{fig:acrobot-orbit}.

The set \(E_\pi := E(\pi,0)\) is outlined in black. 
Because of model mismatch, \(E_\pi\) is no longer the boundary between
rotations and oscillations.
The oscillation domain is actually much larger: orbits rotate once they hit the
\(p_u\)-axis at \(\abs{p_u} \approx 0.15\), while \(E_\pi\) intersects the
\(p_u\)-axis at \(\abs{p_u} \approx 0.055\).
Despite this, the VNHC still injects energy into the acrobot.
The points where the orbit exits \(E_\pi\) are marked with black stars,
with the final departure marked with a red star.
After this final departure, the acrobot begins rotating and continues to gain
energy over time.

\begin{figure}[h]
    \centering
    \begin{subfigure}[t]{0.45\linewidth}
        \includegraphics[width=\linewidth]{acrobot_orbit.png}
        \caption{Orbit initialized at \((q_u,p_u) = (\pi/32,0)\).}
        \label{fig:acrobot-orbit}
    \end{subfigure}
    \begin{subfigure}[t]{0.45\linewidth}
        \includegraphics[width=\linewidth]{acrobot_mc.png}
        \caption{Monte Carlo results.}
        \label{fig:acrobot-mc}
    \end{subfigure}
    \caption{Simulations using Wang's acrobot \cite{xingbo_thesis}.}
\end{figure}

To verify that the acrobot would always achieve rotations, we ran a
Monte-Carlo simulation \cite{montecarlo}:
we initialized the acrobot randomly inside the sublevel set
\[
    \left\{(q_u,p_u) \in \SxR \mid
    E(q_u,p_u) \leq E\left(\frac{\pi}{32},0\right)\right\}
    ,
\] 
and measured the how long it took to begin rotating.
The results in Figure \ref{fig:acrobot-mc} show that
the acrobot always rotated within 10--35 seconds.

\subsection{Physical Experiments}
Wang's acrobot has an encoder at the pivot which measures \(q_u\) and
\(\dot{q}_u\).
The leg actuator is a servo motor with a built-in PID controller, which provides
measurements of \(q_a\).
We estimate \(\dot{q}_a\) through sequential values of \(q_a\) and
compute \(p_u\) through \(p_u = e_1^T M(q) \dot{q}\).
We then assign the actuator value at iteration \(k \in \mathbb{Z}_{> 0}\)
via \(q_a^{k} = \arctan(I p_u^{k-1})\).

\textbf{Baseline Test:} 
for this test, we initialized the acrobot at 
\((q_u,p_u) \approx \left(\frac{\pi}{8},0\right)\). 
The resulting orbit is shown in Figure \ref{fig:acrobot-unperturbed-orbit};
the acrobot is clearly gaining energy over time.

\begin{figure}
    \centering
    \begin{subfigure}[t]{0.45\linewidth}
        \includegraphics[width=\linewidth]{acrobot_unperturbed_orbit.png}
        \caption{The baseline test.}
        \label{fig:acrobot-unperturbed-orbit}
    \end{subfigure}
    \begin{subfigure}[t]{0.45\linewidth}
        \includegraphics[width=\linewidth]{acrobot_stopped_orbit.png}
        \caption{Acrobot orbit before (blue) and after (red) stopping.}
        \label{fig:acrobot-stopped-orbit}
    \end{subfigure}
    \caption{The physical acrobot's orbit during baseline and stop tests.}
\end{figure}

\textbf{Stop Test:}
for this test we initialized the acrobot at 
\((q_u,p_u) \approx \left(\pi,0\right)\), let it run for 15
seconds, then stopped it at the bottom of its arc.
The resulting orbit is shown in Figure \ref{fig:acrobot-stopped-orbit}.
The blue curves correspond to the orbit before the disturbance, while the red
spiral confirms that the acrobot begins oscillating after it is stopped.
Despite the disturbance, it gains energy and eventually starts rotating
again.

\textbf{Push Test:}
to see how the acrobot responds when pushed, we allowed
the acrobot to rotate undisturbed for 15 seconds and then pushed it in its
direction of motion.
The orbit in Figure \ref{fig:acrobot-fpush-orbit} shows that the acrobot speeds
up to rotate with energy \(E(0,0.22)\), but then slows down until it reaches a
stable rotation with energy \(E(0,-0.195)\).
We repeated this test by pushing the acrobot against its direction of motion.
The orbit in Figure \ref{fig:acrobot-rpush-orbit} demonstrates that the acrobot
responds by readily changing direction, and quickly achieves its maximum speed
with energy \(E(0,0.195)\).

These push tests suggest that our VNHC injects energy into Wang's acrobot on
\(\mathcal{O}_2(0.195)\).

\begin{figure}
    \centering
    \begin{subfigure}[ht]{0.45\linewidth}
        \includegraphics[width=\linewidth]{acrobot_fpush_orbit.png}
        \caption{The forwards push test.}
        \label{fig:acrobot-fpush-orbit}
    \end{subfigure}
    \begin{subfigure}[ht]{0.45\linewidth}
        \includegraphics[width=\linewidth]{acrobot_rpush_orbit.png}
        \caption{The reverse push test.}
        \label{fig:acrobot-rpush-orbit}
    \end{subfigure}
    \caption{The acrobot orbit before (blue) and after (red) pushing.}
\end{figure}

\subsection{Summary of Experiments}
These simulations and experiments demonstrate that VNHCs are excellent
tools for injecting energy, even with significant model mismatch.
In particular, energy injection through VNHCs appears to be robust against a
variety of disturbances.

%/========== Proof ==========/%
\section{Proof of Theorem \ref{thm:acrobot-energy-stabilization}}\label{sec:proof}

%/========== Conclusion ==========/%
\section{Conclusion}\label{sec:conclusion}
In this article we summarized the existing theory of virtual nonholonomic
constraints (VNHCs) ........
\textbf{TODO conclude nicely}
In the end, we demonstrated that virtual nonholonomic constraints are capable of
injecting and dissipating energy in a robust manner, all while producing
realistic biological motion.
